### 2017-12-02 README.Rmd

@@

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("Zouter/dynalysis", dependencies = TRUE, upgrade_dependencies = TRUE)
```

>>>>

### Dependencies

You might have to install a few packages.

Ubuntu/Debian:
```
sudo apt-get install libudunits2-dev libgsl-dev libsdl1.2-dev libreadline-dev imagemagick libfftw3-dev libudunits2-dev -y
sudo apt-get install python2.7-dev python3-dev python3-pip
pip3 install --user virtualenv numpy matplotlib pandas six jinja2 python-dateutil pytz pyparsing cycler tqdm python-igraph rpy2 Cython scipy statsmodels sklearn seaborn
```

Fedora/CentOS:
```
sudo dnf install openssl-devel libcurl-devel udunits2-devel libxml2-devel gsl-devel SDL2-devel readline-devel ImageMagick-c++-devel SDL-devel python2-devel python3-devel python3-pip
pip3 install --user virtualenv numpy matplotlib pandas six jinja2 python-dateutil pytz pyparsing cycler tqdm python-igraph rpy2 Cython scipy statsmodels sklearn seaborn
Rscript -e 'install.packages("udunits2", configure.args =  c(udunits2 = '--with-udunits2-include=/usr/include/udunits2'))'
```

@@

```{r gh-installation, eval = FALSE}
install.packages("remotes")
options(repos = c("https://cran.rstudio.com/", "http://bioconductor.org/packages/release/bioc/", "http://bioconductor.org/packages/release/data/annotation", "http://bioconductor.org/packages/release/data/experiment", "http://bioconductor.org/packages/release/extra"))
remotes::install_github("Zouter/dynalysis", dependencies = TRUE)
```
